---
title: "Streeter_Phelps_Model"
output: 
  word_document: default
  html_notebook: default
  html_document: default
---

```{r}
rm(list = ls()) #Command to clean all the data
library(deSolve) #Library used to solve differential equations
```

#1.Modification of Streeter-phelps equations, using the Thomas Model
```{r}
model= function(t, y, p) {
  list(c(
    BOD = -(p$k1-p$k3) * y[["BOD"]], #Implementation of Thomas Model (Equation 9 from Tutorial)
    DO = -p$k1 * y[["BOD"]] * p$s + p$k2 * (DO_sat(p$temp) - y[["DO"]]) 
    ))
  }
```

This aspect defines O2 saturation as a function of temperature:
```{r}
DO_sat= function(T) {14.652 - 0.41022*T + 0.007991*T^2 - 7.7774e-5*T^3}
```

This aspects determines the values of k2
```{r}
u = 0.3 #Kindly Note: Flow velocity were taken to be 0.1, 0.5, & 0.7 to observe the effects on oxygen conc.
h = 3 #Water depth
T = 20 #Water temperature
k2 = ((3.09*u^0.5)*(1.025^(T-20))^0.5)/(h^0.5)
```


Define parameters (p), initial values (y0), and times of interest (times):
```{r}
p = list(k1= 0.2, #Organic matter coefficient
         k2= k2, 
         s=3, 
         k3=0.1,
         temp= 20) 
y0 = c(BOD=10,
       DO=DO_sat(p$temp)) 

times = seq(0, 30, by = 1) 
```

#Finding Numerical Solution
```{r}
res_new = lsoda(y = y0, 
            times = times, 
            func = model, 
            parms = p) 
```

#Plotting the Results
```{r}
plot(res_new[,2], type="l", col="red", lwd=2, xlab="", ylab="", ylim=c(0,10), xlim=c(2,30)) #[,2] refers to row 2
lines(as.vector(res_new[,3]), type="l", lwd=2, lty = "dashed")
grid()
title(ylab=expression("Concentration"~ ~"["~mg/dm^3~"]"),line=2, cex.lab=1)
title(xlab = expression("Time [days]", line=1, cex.lab=1)) 
title(main = "Numerical solution for BOD-DO Using Thomas Model")
legend("topright", legend=c("BOD", "DO"), col=c("black", "red"), lwd=c(2,2), ncol=1)
dev.copy(png,"Figures/Figure1.png", units='in', width=8.5,height=6,res=1200)
dev.off()
```

```{r}
write.table(res_new, file="thomasatBOD10_New.csv", sep=",")
```

#Evaluating K2 as a function of Temperature
```{r}
u = 0.3 #Flow velocity
T = seq(0,30,by=1) #Water temperature
h = 3 #Water depth
k2 = ((3.09*u^0.5)*(1.025^(T-20))^0.5)/(h^0.5)
```

#Plotting the result 
```{r}
plot(T,k2,type="l",col="red",lwd=2,xlab="",ylab="")
grid()
title(ylab=expression("k2"~~"["~1/d~"]"),line=2, cex.lab=1)
title(xlab = expression("Temperature"~~"["~degree~c~"]"),line=2,cex.lab=1)
title(main = "K2 as a fucntion of T")
legend("bottomright", legend=c("Aeration coefficient"), col=c("red"), lwd=c(2), ncol=1)
dev.copy(png,"Figures/Figure2.png", units='in', width=8.5,height=6,res=1200)
dev.off()
